### 2019-08-08 defesa/tex/appendix/3pnts_ellipse_1.tex
wip

As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator), after multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.

>>>>

As $||\varphi(p_2)||^2$ has degree $4$ and $\varphi(p_3)_y$ has degree $2$ (ignoring the denominator). After multiplying and squaring we arrive at the conclusion that the polynomial has degree $12$.

### 2019-08-08 defesa/tex/chapter/ellipses_n.tex
wip

	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses. As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertice. Selecting any of these vertices as $q_j'$ will make $|\Pp \cap E_j(q_j', \theta_j)| \ge 2$.

@@

The second case says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$ the covered set will stay the same.

@@

As a consequence of \autoref{lema:3pnts}, from any optimal solution of $MCER$ it is possible to obtain another optimal solution which every ellipse has one, two or three points on its border.
This result cuts the search space to $\bigO(mn^3)$ which is a very nice gain from where we started, with a infinite search space. Breaking down every possible case, for every ellipse in an optimal solution we obtain:

\begin{itemize}
	\item The ellipse covers only one point. You could place the ellipse so it has one point on its border, satisfying the claim above.
	\item The ellipse covers exactly two points. Using \autoref{lema:mce_2b}, there is a solution with those two points on the border.
	\item The ellipse covers more than two points. First we can use \autoref{lema:mce_2b} to fix two points on the border. By \autoref{lema_3} the angle can be ignored as long as the two fixed points are on the border or exists another optimal solution with three (or more) points on the border.
\end{itemize}

From those cases, three sub-problems need to be solved so we can have a method for $MCER$.

The first one is covering one point with an ellipse which is trivial. For a point $(x, y) \in \R$ just set the center of the ellipse to be $(x, y) \in \R$.

The second problem and third problems deserve sections on their own.

\section{Two points on the border}

Because of the case 2 of \autoref{lema:3pnts}, we want to find for every pair of points the set of points an ellipse with them on its border can cover

>>>>

	As it was shown on \autoref{chapter:ellipses}, $X$ is a region that is limited by arcs of ellipses. As this region is the non-empty intersection of more than one ellipse, there are at least two of these arcs that encounter at one point creating a vertice. Selecting any of these vertices as $q_j'$ will make $|\Pp \cap \tilde{E}_j(q_j', \theta_j)| \ge 2$.

@@

The second case of \autoref{lema:3pnts} says that after fixing a pair of points on the border of $E_j$ maintaining the covered set, for any angle that allows the two points to stay on the border of $E_j$, there is a center that maintains the covered set the same.

@@

If we define an equivalence relation between optimal solutions as: $S_1$ is equivalent to $S_2$ if they both cover the same set of points, we can use \autoref{lema:3pnts} and \autoref{lema:mce_2b} to identify the equivalence classes. Let $S$ be any optimal solution, in $[S]$ (its equivalence class) there is another solution where any ellipse $E_j \in \E$ falls in at least one of the cases below:

\begin{itemize}
	\item $E_j$ covers only on point.
	\item $E_j$ covers more than one point with $u$ and $v$ being on the border of $E_j$. Note that there could be infinitely many of solutions like that, however \autoref{lema:3pnts} guarantees that any $(E_j, u, v)$-feasible angle yields an equivalent optimal solution.
	\item $E_j$ covers more than two points with three of them on its border.
\end{itemize}

The following two sections will treat the second and third cases (the first case is trivial). Going through every possibility of an ellipse falling in any of the three cases guarantees that an optimal solution is found.

\section{Ellipse by two points}

Let $E$ be an ellipse with shape parameters $(a, b)\in \R^2_{>0}$ and $u, v\in \R^2$, one wants to find a $(E, u, v)$-feasible angle $\theta\in[0,\pi]$ and every center $q\in\R^2$ such that $\{u, v\} \subset \tilde{E}(q, \theta)$.

For a fixed angle, finding every center such that two points are on the border of the ellipse is done on \autoref{chapter:ellipses_intersection}, from there we know that there could be at most $2$ of such centers.
